### 2019-07-09 paper.tex
main files for paper submission uploaded

\section{Bayesian hierarchical modeling}
\label{sec:hbm}
A Bayesian hierarchical model (BHM) provides a flexible setting for modeling categorical data that allows for heterogeneity across individuals or groups. If homogeneity across studies is assumed, the data can be combined via Bayesian updating as in the sequential analysis in the previous section.  All that is needed are the number of occurrences, $s_i$, in $n_i$ subjects in each study, $i$, of $N$ studies.  he posterior distribution is then 
\begin{equation}
\begin{split}
p(\theta | s_1,...,s_N, n_1,...,n_N,a,b) = \\ \textnormal{Beta}(\sum_{i=1}^N (s_i +a),\sum_{i=1}^N(n_i - s_i) + b),
\end{split}
\label{eq:pbeta}
\end{equation}
with $a=b=1$ for a uniform prior for $\theta$.
\vskip 6pt
Alternatively, BHM can be specified to allow for heterogeneity across studies due to different trial sites, different types of treatment, such as different families of anxiety medication (SSRI or SNRI), etc., and the same Bayesian machinery can be employed to compare a variety of treatments relative to placebo. For the categorical data examined herein there are two common BHM specifications: the Beta-Gamma,\cite{Kruschke2014} and the logistic-normal.\cite{Mcelreath2015}.  In the following, we adopted the Beta-Gamma BHM specification as it directly provides intuitively understandable parameter estimates, whereas the logistic specification is more difficult to interpret.
\vskip 6pt
The complete BHM Beta-Gamma modeling framework is illustrated in Figure \ref{fig:bhm} for the case of comparing two sets of RCTs for different treatments (SSRI vs. SNRI) with placebo groups in each RCT. Each study in Figure \ref{fig:bhm} has a Binomial likelihood for $s$ successes in $n$ trials with probability of success $\theta$ (row 3).  A Beta prior with mode $\omega$ and precision parameter $K$ is assigned to each $\theta$ (row 2), and a Beta and Gamma hierarchical prior are assigned to $\omega$ and $K$ respectively (row 1). The hyperparameters $a,b,d$ and $r$ are selected to represent a priori knowledge about the distribution of each $\theta$ (typically relatively uninformative priors are assigned unless other information is available).
\vskip 6pt
The package Turing.jl provides HMC and MCMC algorithms to obtain posterior density MCMC chains from an essentially unlimited variety of models through Julia macros that provide a flexible and intuitive modeling and inference framework. The model specification in Turing.jl closely matches how one would write the model mathematically (Turing code examples for the logistic-normal are available at github.com/TuringLang/Turing.jl and github.com/StatisticalRethinkingJulia):

\begin{lstlisting}[language = Julia]
# Turing.jl BHM for binomial trials
using Turing, MCMCChains

@model binomial_trials(s,n) = begin
g = length(n)  # number of groups
# hierarchical priors
w ~ Beta(2,3)
KappaMinusTwo ~ Gamma(10,1/0.05) 
a = w*KappaMinusTwo + 1.0
b = (1.0 - w)*KappaMinusTwo+1.0
# priors for each occurrence rate
theta = Array{Real}(undef, g)
for k in 1:g
theta[k] ~ Beta(a,b)
end
# likelihood
for i in 1:g
s[i] ~ Binomial(n[i],theta[i])
end
end;
\end{lstlisting}

>>>>

\section{Bayesian hierarchical modeling}
\label{sec:hbm}
A Bayesian hierarchical model (BHM) provides a flexible setting for modeling categorical data that allows for heterogeneity across individuals or groups. If homogeneity across studies is assumed, the data can be combined via Bayesian updating as in the sequential analysis in the previous section.  All that is needed are the number of occurrences, $s_i$, in $n_i$ subjects in each study, $i$, of $N$ studies.  he posterior distribution is then 
\begin{equation}
\begin{split}
p(\theta | s_1,...,s_N, n_1,...,n_N,a,b) = \\ \textnormal{Beta}(\sum_{i=1}^N (s_i +a),\sum_{i=1}^N(n_i - s_i) + b),
\end{split}
\label{eq:pbeta}
\end{equation}
with $a=b=1$ for a uniform prior for $\theta$.
\vskip 6pt
Alternatively, BHM can be specified to allow for heterogeneity across studies due to different trial sites, different types of treatment, such as different families of anxiety medication (SSRI or SNRI), etc., and the same Bayesian machinery can be employed to compare a variety of treatments relative to placebo. For the categorical data examined herein there are two common BHM specifications: the Beta-Gamma,\cite{Kruschke2014} and the logistic-normal.\cite{Mcelreath2015}.  In the following, we adopted the Beta-Gamma BHM specification as it directly provides intuitively understandable parameter estimates, whereas the logistic specification is more difficult to interpret.
\vskip 6pt
The complete BHM Beta-Gamma modeling framework is illustrated in Figure \ref{fig:bhm} for the case of comparing two sets of RCTs for different treatments (SSRI vs. SNRI) with placebo groups in each RCT. Each study in Figure \ref{fig:bhm} has a Binomial likelihood for $s$ successes in $n$ trials with probability of success $\theta$ (row 3).  A Beta prior with mode $\omega$ and precision parameter $K$ is assigned to each $\theta$ (row 2), and a Beta and Gamma hierarchical prior are assigned to $\omega$ and $K$ respectively (row 1). The hyperparameters $a,b,d$ and $r$ are selected to represent a priori knowledge about the distribution of each $\theta$ (typically relatively uninformative priors are assigned unless other information is available).
\vskip 6pt
The package Turing.jl provides HMC and MCMC algorithms to obtain posterior density MCMC chains from an essentially unlimited variety of models through Julia macros that provide a flexible and intuitive modeling and inference framework. The model specification in Turing.jl closely matches how one would write the model mathematically (Turing code examples for the logistic-normal are available at github.com/TuringLang/Turing.jl and github.com/StatisticalRethinkingJulia):
\begin{lstlisting}[language = Julia]
# Turing.jl BHM for binomial trials
using Turing, MCMCChains
@model binomial_trials(s,n) = begin
g = length(n)  # number of groups
# hierarchical priors
w ~ Beta(2,3)
KappaMinusTwo ~ Gamma(10,1/0.05) 
a = w*KappaMinusTwo + 1.0
b = (1.0 - w)*KappaMinusTwo+1.0
# priors for each occurrence rate
theta = Array{Real}(undef, g)
for k in 1:g
theta[k] ~ Beta(a,b)
end
# likelihood
for i in 1:g
s[i] ~ Binomial(n[i],theta[i])
end
end;
\end{lstlisting}
